Blockchain System

### 2020-08-25 papers/execution-model/model.tex
cleanup halfway

\begin{definition}[Manager]
An manager manages accounts on the blockchain. It is represented by a
tuple $\langle  \PUK, \PKH, \BAL, \COU \rangle $, where  $\PUK$ is the
public key of an account, $\PKH$ is its public key hash, $\BAL$ is its
balance and $\COU$ is its counter whose form is a pair ($\mathbf{n},
\mathbf{b}$), where $\mathbf{n}$ is a nature number and $\mathbf{b}$
is a boolean value.  
\end{definition}

\begin{definition}[Contractor]
  A contractor manages smart contracts on the blockchain. It is
  represented by a tuple
  $\langle \PUH, \BAL, \CODE, \STORAGE \rangle $, where $\PUH$ is the
  public hash of the contract, $\BAL$ is its balance, $\CODE$ is its
  code and $\STORAGE$ is its storage.
\end{definition}

\begin{definition}[Operation]
An operation is expressed as the following syntax:
\\
$\OP$ ::= transfer  $\mathbf{n}$ from $\PKH$ to $\PKH'$ fee $\mathbf{m}$
%\\$\mid$ register key $\PKH$ as delegate fee $\mathbf{m}$ 
%\\$\mid$ set delegate for $\PKH$ to $\PKH'$  fee $\mathbf{m}$ 
%\\$\mid$ withdraw delegate from $\PKH$ fee $\mathbf{m}$ 
\\$\mid$ originate contract $\mathbf{id}$ transferring  $\mathbf{n}$ from $\PKH$ running $\CODE$ init $\mathbf{s}$ fee $\mathbf{m}$
\\$\mid$ transfer $\mathbf{n}$ from $\PKH$ to  $\PUH$ arg $\mathbf{s}$ fee $\mathbf{m}$
\end{definition}

\begin{definition}[Query]
An query is expressed as the following syntax:
\\
$\mathbf{qry}$ ::= get balance for $\PKH / \PUH$
%$\mid$ get delegate for $\PKH$
\\$\mid$ get status for $\OPH$ 
\\$\mid$ get contract storage $\PUH$ 
\\$\mid$ get code for $\PUH$ 
%\\$\mid$ waiting for $\OPH$ to be included in $\mathbf{m}$ blocks
%\\$\mid$ get timestamp
%\\$\mid$ get contracts
%\\$\mid$ show contracts for $\PKH$
\\$\mid$ get public key for $\PKH$
%\\$\mid$ get balance for $\PKH$
\\$\mid$ get counter for $\PKH$

\end{definition}
 \begin{definition}[State of a node]
   The state of a node is a tuple
   $[\mathbf{C}, \mathbf{O}, \mathbf{S}]$ where $\mathbf{C}$ is a set of accounts,
   $\mathbf{O}$ a set of operations, and $\mathbf{S}$  a set of contracts. 
\end{definition}

When an operation is injected in a node, it enters in a pending pool
(and is called a pending operation). 
 \begin{definition}[Pending operation]
A pending operation is a tuple  $\langle  \OP, \OPH, \TIME
\rangle $, where $\OP$ is an operation, $\OPH$ is the operation hash
and $\TIME$ is the time when the operation was injected. 
\end{definition}
After some time, a pending operation may be included in the blockchain as an accepted operation.
%Let \textit{P} is the set of pending operations.
 \begin{definition}[Accepted operation]
An accepted operation  is expressed as a tuple $\langle  \OP, \OPH, \TIME \rangle $, where $\OP$ is an operation, $\OPH$ is the operation hash and $\TIME$ is the time when it is included in the blockchain. 
\end{definition}

@@

\begin{definition}[Blockchain system]
A blockchain system is a pair
$\mathbf{S} \triangleq\langle \mathbf{M}, \mathbf{B} \rangle$ where
\begin{enumerate}
\item $\mathbf{M} = [C, O, S]$ is the state of a node, and
\item $\mathbf{B} = [P, A, K, T, t]$ is the state of a blockchain 
  such that $\forall c \in C \implies \exists k\in K, k.pkh = c.pkh$
  and $\forall s \in S \implies \exists p \in T, s.puh = p.puh$.
\end{enumerate}
\end{definition}

@@

\begin{equation}{}
\frac{\text{checkAcc($pkh$, C)}}{\parbox{4.2in}{\text{$\langle$[C, O, S], [P, A, K, T, t]$\rangle \rightarrow \langle$[C, (transfer $n$ from $pkh$ to $pkh'$ fee $m$)} ~\\\text{ :: O, S], [P, A, K, T, t]$\rangle$}}} 
\end{equation}
~\\
~\\
Rule 2 [injected]:

\begin{equation}{}
\frac{\text{checkBan(K, $pkh, n, m$) $\wedge$ checkCou(K, $pkh$) $\wedge$ checkPub(K, $pkh'$)}}{\parbox{4.2in}{\text{$\langle$[C, (transfer $n$ from $pkh$ to $pkh'$ fee $m$) :: O, S], [P, A, K, T, t]$\rangle \rightarrow$}\\
\text{$\langle$[C, O, S], [($<$ transfer $n$ from $puk$ to $puk'$ fee $m$, generateOph($pkh$, }\\
\text{$pkh', n, m$, t), t $>$) :: P, A, updateCou(K, $pkh$, True), T, t]$\rangle$}}} 
\end{equation}
~\\
~\\
Rule 3 [rejected of counter]:

\begin{equation}{}
\frac{\text{$\neg$ checkCou(K, $pkh$)}}{\parbox{4.2in}{\text{$\langle$[C, (transfer $n$ from $pkh$ to $pkh'$ fee $m$) :: O, S], [P, A, K, T, t]$\rangle \rightarrow$ }\\
\text{$\langle$[C, O, S], [P, A, K, T, t]$\rangle$}}} 
\end{equation}
~\\
~\\
Rule 4 [rejected of balance]:

\begin{equation}{}
\frac{\text{$\neg$ checkBan(K, $pkh, m, n$)}}{\parbox{4.2in}{\text{$\langle$[C, (transfer $n$ from $pkh$ to $pkh'$ fee $m$) :: O, S], [P, A, K, T, t]$\rangle \rightarrow$ }\\
\text{$\langle$[C, O, S], [P, A, K, T, t]$\rangle$}}} 
\end{equation}
~\\
~\\
Rule 5 [rejected of public key]:

\begin{equation}{}
\frac{\text{$\neg$ checkPub(K, $pkh'$)}}{\parbox{4.2in}{\text{$\langle$[C, (transfer $n$ from $pkh$ to $pkh'$ fee $m$) :: O, S], [P, A, K, T, t]$\rangle \rightarrow$ }\\
\text{$\langle$[C, O, S], [P, A, K, T, t]$\rangle$}}} 
\end{equation}
~\\
~\\
Rule 6 [included]:
\begin{equation}{}
\frac{}{\parbox{4.2in}{\text{[$<$ transfer $n$ from $puk$ to  $puk'$ fee $m$, oph, t $>$ :: P, A, K, T, t' ] $\rightarrow$ } \\
 \text{[P, $<$ transfer $n$ from  $puk$ to $puk'$ fee $m$, oph, t' $>$ :: A, updateSucc(K, } \\
\text{$puk, puk', n, m$), T, t' + 1]}}} 
\end{equation}
~\\
Rule 7 [timeout]:
\begin{equation}{}
\frac{\text{t' - t $\ge$ 60}}{\parbox{4.2in}{\text{[$<$ transfer $n$ from $puk$ to  $puk'$ fee $m$, oph, t $>$ :: P, A, K, T, t' ] $\rightarrow$} \\
 \hspace*{0cm} \text{[P, A, updateCou(K, $puk$, False), T, t']}}} 
\end{equation}

@@

\begin{equation}{}
\frac{\text{checkAcc($pkh$, C) $\wedge$ checkId($id$, S)}}{\parbox{4.2in}{\text{$\langle$[C, O, S], [P, A, K, T, t]$\rangle \rightarrow \langle$[C, (originate contract ${id}$ transferring} \\
  \text{${n}$ from ${pkh}$} \text{running ${code}$ init ${s}$) :: O, S], [P, A, K, T, t]$\rangle$}}} 
\end{equation}
~\\
~\\
Rule 2 [injected]:

\begin{equation}{}
\frac{\text{checkBan(K, $pkh, n, m$) $\wedge$ checkCou(K, $pkh$) $\wedge$ \text{checkPrg($code, s$)}}}{\parbox{4.2in}{\text{$\langle$[C, (originate contract ${id}$ transferring  ${n}$ from ${pkh}$ running ${code}$ init ${s}$)} \text{ :: O, S], [P, A, K, T, t] $\rangle \rightarrow \langle$ [C, O, S],} \text{[(originate contract ${id}$ transferring ${n}$ from ${pkh}$ running ${code}$ init ${s}$)} \text{:: P, A, updateCou(K, $pkh$, True), T, t] $\rangle$}}} 
\end{equation}
~\\
~\\
Rule 3 [rejected of code]:

\begin{equation}{}
\frac{\text{$\neg$ checkPrg($code, s$)}}{\parbox{4.2in}{\text{$\langle$[C, (originate contract ${id}$ transferring  ${n}$ from ${pkh}$ running ${code}$ init ${s}$)} \text{:: O, S], [P, A, K, T, t]$\rangle \rightarrow \langle$[C, O, S],} \text{[P, A, K, T, t]$\rangle$}}} 
\end{equation}
~\\
~\\
Rule 4 [rejected of counter]:

\begin{equation}{}
\frac{\text{$\neg$ checkCou(K, $pkh$)}}{\parbox{4.2in}{\text{$\langle$[C, (originate contract ${id}$ transferring  ${n}$ from ${pkh}$ running ${code}$ init ${s}$))} \text{:: O, S], [P, A, K, T, t]$\rangle \rightarrow \langle$ [C, O, S],} \text{[P, A, K, T, t]$\rangle$}}} 
\end{equation}
~\\
~\\
Rule 5 [rejected of balance]:

\begin{equation}{}
\frac{\text{$\neg$ checkBan(K, $pkh, n, m$)}}{\parbox{4.2in}{\text{$\langle$[C, (originate contract ${id}$ transferring  ${n}$ from ${pkh}$ running ${code}$ init ${s}$)} \text{:: O, S], [P, A, K, T, t]$\rangle \rightarrow \langle$[C, O, S],} \text{[P, A, K, T, t]$\rangle$}}} 
\end{equation}
~\\
~\\
Rule 6 [included]:
\begin{equation}{}
\frac{}{\parbox{4.2in}{\text{$\langle$[C, O, S], [$<$ (originate contract ${id}$ transferring  ${n}$ from ${pkh}$ running } \\
\text{${code}$ init ${s}$), t $>$ :: P, A, K, T, t' ]$\rangle \rightarrow \langle$[C, O,($< id$, } \\
\text{generateHash($id, code, s$, t'), $code >$ :: S)], [P, $<$ (originate contract ${id}$ } \\
\text{transferring  ${n}$ from ${pkh}$ running ${code}$ init ${s}$), t' $>$ :: A, updateSucc(K, } \\
\text{$puk, n, m$), ($<$ generateHash($id, code, s$, t'), $n, code$, } \\
 \text{getStorage($code, s$) $>$) :: T), t' + 1]$\rangle$}}} 
\end{equation}
~\\
Rule 7 [timeout]:
\begin{equation}{}
\frac{\text{t' - t $\ge$ 60}}{\parbox{4.2in}{\text{[$<$ (originate contract ${id}$ transferring  ${n}$ from ${pkh}$ running ${code}$ init ${s}$) $>$ } \\
\text{:: P, A, K, T, t' ] $\rightarrow$[P, A, updateCou(K, $puk$, False), T, t']}}} 
\end{equation}
~\\
~\\
B. \textbf{Transfer}
\\
~\\
Rule 1 [proposal]:

\begin{equation}{}
\frac{\text{checkAcc($pkh$, C)  }}{\parbox{4.2in}{\text{$\langle$[C, O, S], [P, A, K, T, t]$\rangle \rightarrow \langle$[C, (transfer ${n}$ from ${pkh}$ to  ${puh}$ arg ${s}$ }  \\
\text{fee ${m}$) :: O, S], [P, A, K, T, t]$\rangle$}}} 
\end{equation}
~\\
~\\
Rule 2 [injected]:

\begin{equation}{}
\frac{\text{checkBan(K, $pkh, n, m$) $\wedge$ checkCou(K, $pkh$) $\wedge$ checkPuh(T, $puh$)}
\\
\text{ $\wedge$ checkArg(T, $puh, s$)}}{\parbox{4.2in}{\text{$\langle$[C, (transfer ${n}$ from ${pkh}$ to  ${puh}$ arg ${s}$ fee ${m}$) :: O, S], [P, A, K, T, t]$\rangle$}\\
\text{$\rightarrow$  $\langle$[C, O, S], [($<$ (transfer ${n}$ from ${pkh}$ to  ${puh}$ arg ${s}$ fee ${m}$), }\\
 \text{generateOph($pkh, puh, s, n, m$, t), t $>$) :: P, A, updateCou(K, $pkh$, True), }\\
\text{T, t] $\rangle$}}} 
\end{equation}
~\\
~\\
Rule 3 [rejected of counter]:

\begin{equation}{}
\frac{\text{$\neg$ checkCou(K, $pkh$)}}{\parbox{4.2in}{\text{$\langle$[C, (transfer ${n}$ from ${pkh}$ to  ${puh}$ arg ${s}$ fee ${m}$) :: O, S], [P, A, K, T, t]$\rangle$  }\\
\text{$\rightarrow \langle$[C, O, S], [P, A, K, T, t]$\rangle$}}} 
\end{equation}
~\\
~\\
Rule 4 [rejected of balance]:

\begin{equation}{}
\frac{\text{$\neg$ checkBan(K, $pkh, n, m$)}}{\parbox{4.2in}{\text{$\langle$[C, (transfer ${n}$ from ${pkh}$ to  ${puh}$ arg ${s}$ fee ${m}$) :: O, S], [P, A, K, T, t]$\rangle$ }\\
\text{$\rightarrow \langle$[C, O, S], [P, A, K, T, t]$\rangle$}}} 
\end{equation}
~\\
~\\
Rule 5 [rejected of public hash]:

\begin{equation}{}
\frac{\text{$\neg$ checkPuh(T, $puh$)}}{\parbox{4.2in}{\text{$\langle$[C, (transfer ${n}$ from ${pkh}$ to  ${puh}$ arg ${s}$ fee ${m}$) :: O, S], [P, A, K, T, t]$\rangle$ }\\
\text{$\rightarrow \langle$[C, O, S], [P, A, K, T, t]$\rangle$}}} 
\end{equation}
~\\
~\\
Rule 6 [rejected of argument]:

\begin{equation}{}
\frac{\text{$\neg$ checkArg(T, $puh, s$)}}{\parbox{4.2in}{\text{$\langle$[C, (transfer ${n}$ from ${pkh}$ to  ${puh}$ arg ${s}$ fee ${m}$) :: O, S], [P, A, K, T, t]$\rangle$}\\
\text{$\rightarrow \langle$[C, O, S], [P, A, K, T, t]$\rangle$}}} 
\end{equation}
~\\
~\\
Rule 7 [included]:

\begin{equation}
\frac{}{
  \begin{array}{l}
\text{[$<$ transfer $n$ from $puk$ to  $puh$ fee $m$, oph, t $>$ :: P, A, K, T, t' ] $\rightarrow$ } \\
\text{[P, $<$ (transfer ${n}$ from ${pkh}$ to  ${puh}$ arg ${s}$ fee ${m}$), oph, t' $>$ :: A, } \\
\text{updateSucc(K, puk, '', $n, m$), updateConstr(T, $puh, n$,
  $s$), $t' + 1$]}
  \end{array}
}\label{eq:1}
\end{equation}
~\\
Rule 8 [timeout]:
\begin{equation}{}
\frac{\text{t' - t $\ge$ 60}}{\parbox{4.2in}{\text{[transfer $n$ from $puk$ to  $puh$ fee $m$, t $>$ :: P, A, K, T, t' ] $\rightarrow$} \\
\text{[P, A, updatecou(K, $puk$, False), T, t']}}} 
\end{equation}

\section{Functions}
\begin{enumerate}
    \item Function \verb!checkAcc(pkh, C)! checks whether an account $pkh$ exists in C
    \item Function \verb!checkPub(K, pkh)! checks whether the public key of the public key hash $pkh$ is reveled to the blockchain.
    \item Function \verb!checkBan(K, pkh, n, m)! checks whether the balance of the account $pkh$ is greater or equal to $m$ + $n$
    \item Function \verb!checkCou(K, pkh)! checks whether the current counter of an account $phk$ is used
    \item Function \verb!updateSuc(K, pkh, pkh', n, m)! updates the balance and the counter of the account $phk$ and the balance of the account $phk'$, where
    \begin{itemize}
        \item  \verb!< puk, pkh, bal, (n, True) >!  \verb!=>! \\ \verb!< puk, pkh, bal - n - m, (n + 1, False) >!
        \item  \verb!< puk', pkh', bal', cou' >! \verb!=>! \verb!< puk', pkh', bal' + n, cou' >!
    \end{itemize}

>>>>

\begin{definition}[Manager]
A manager manages a single account. It is represented by a
tuple $\langle  \PUK, \PKH, \BAL, \COU \rangle $, where  $\PUK$ is the
public key of an account, $\PKH$ is its public key hash, $\BAL$ is its
balance and $\COU$ is its counter whose form is a pair $(n, b)$, where $n$ is a natural number and ${b}$
is a boolean value.  
\end{definition}

\begin{definition}[Contractor]
  A contractor manages a smart contract. It is
  represented by a tuple
  $\langle \PUH, \BAL, \CODE, \STORAGE \rangle $, where $\PUH$ is the
  public key hash of the contract, $\BAL$ is its current balance, $\CODE$ is its
  code, and $\STORAGE$ is its current storage.
\end{definition}

\begin{definition}[Operation]
  Operations are defined by the following grammar:
  \begin{align*}
    \OP &::= \TRANSFER[\STRING]\NTEZ\PKH{\PKH'}\MTEZ
    \\&\mid \ORIGINATE\ID\NTEZ\PKH\CODE\STRING\MTEZ
    % \\&\mid transfer $\mathbf{n}$ from $\PKH$ to  $\PUH$ arg $\mathbf{s}$ fee $\mathbf{m}$
  \end{align*}
%\\$\mid$ register key $\PKH$ as delegate fee $\mathbf{m}$ 
%\\$\mid$ set delegate for $\PKH$ to $\PKH'$  fee $\mathbf{m}$ 
%\\$\mid$ withdraw delegate from $\PKH$ fee $\mathbf{m}$ 
\end{definition}

\begin{definition}[Query]
Queries are defined by the following grammar:
\begin{align*}
  \QRY & ::= \GETBALANCE {\PKH / \PUH}
  \\&\mid \GETSTATUS\OPH
  \\&\mid \GETSTORAGE\PUH
  \\&\mid \GETCODE\PUH 
  \\&\mid \GETPUBLICKEY\PKH
  \\&\mid \GETCOUNTER\PKH
\end{align*}

%$\mid$ get delegate for $\PKH$
%\\$\mid$ waiting for $\OPH$ to be included in $\mathbf{m}$ blocks
%\\$\mid$ get timestamp
%\\$\mid$ get contracts
%\\$\mid$ show contracts for $\PKH$
%\\$\mid$ get balance for $\PKH$

\end{definition}
 \begin{definition}[State of a node]
   The state of a node is a tuple
   $[\ACCOUNTS, \OPERATIONS, \CONTRACTS]$ where $\ACCOUNTS$ is a set of accounts,
   $\OPERATIONS$ a set of operations, and $\CONTRACTS$  a set of contracts. 
\end{definition}

When an operation is injected in a node, it enters a \emph{pending pool}
(and is called a pending operation). 
 \begin{definition}[Pending operation]
A pending operation is a tuple  $\langle  \OP, \OPH, \TIME
\rangle $, where $\OP$ is an operation, $\OPH$ is the operation hash
and $\TIME$ is the time when the operation was injected. 
\end{definition}
After some time, a pending operation may be included in the blockchain as an accepted operation.
%Let \textit{P} is the set of pending operations.
 \begin{definition}[Accepted operation]
An accepted operation  is a tuple $\langle  \OP, \OPH, \TIME \rangle
$, where $\OP$ is an operation, $\OPH$ is the operation hash and
$\TIME$ is the time when it was included in the blockchain. 
\end{definition}

@@

\begin{definition}[Blockchain system]
A blockchain system is a pair
$\langle \mathbf{M}, \mathbf{B} \rangle$ where
\begin{enumerate}
\item $\mathbf{M} = [\ACCOUNTS, \OPERATIONS, \CONTRACTS]$ is the state of a node, and
\item $\mathbf{B} = [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$ is the state of a blockchain 
  such that $\forall c \in \ACCOUNTS \implies \exists k\in \MANAGERS, k.pkh = c.pkh$
  and $\forall s \in \CONTRACTS \implies \exists p \in \CONTRACTORS, s.puh = p.puh$.
\end{enumerate}
\end{definition}

@@

\begin{equation}{}
\frac{\text{checkAcc($pkh$, \ACCOUNTS)}}{\parbox{4.2in}{\text{$\langle$[\ACCOUNTS, \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle \rightarrow \langle$[\ACCOUNTS, (transfer $n$ from $pkh$ to $pkh'$ fee $m$)} ~\\\text{ :: \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle$}}} 
\end{equation}
~\\
~\\
Rule 2 [injected]:

\begin{equation}{}
\frac{\text{checkBan(\MANAGERS, $pkh, n, m$) $\wedge$ checkCou(\MANAGERS, $pkh$) $\wedge$ checkPub(\MANAGERS, $pkh'$)}}{\parbox{4.2in}{\text{$\langle$[\ACCOUNTS, (transfer $n$ from $pkh$ to $pkh'$ fee $m$) :: \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle \rightarrow$}\\
\text{$\langle$[\ACCOUNTS, \OPERATIONS, \CONTRACTS], [($<$ transfer $n$ from $puk$ to $puk'$ fee $m$, generateOph($pkh$, }\\
\text{$pkh', n, m$, \TIME), \TIME $>$) :: \PENDING, \ACCEPTED, updateCou(\MANAGERS, $pkh$, True), \CONTRACTORS, \TIME]$\rangle$}}} 
\end{equation}
~\\
~\\
Rule 3 [rejected of counter]:

\begin{equation}{}
\frac{\text{$\neg$ checkCou(\MANAGERS, $pkh$)}}{\parbox{4.2in}{\text{$\langle$[\ACCOUNTS, (transfer $n$ from $pkh$ to $pkh'$ fee $m$) :: \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle \rightarrow$ }\\
\text{$\langle$[\ACCOUNTS, \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle$}}} 
\end{equation}
~\\
~\\
Rule 4 [rejected of balance]:

\begin{equation}{}
\frac{\text{$\neg$ checkBan(\MANAGERS, $pkh, m, n$)}}{\parbox{4.2in}{\text{$\langle$[\ACCOUNTS, (transfer $n$ from $pkh$ to $pkh'$ fee $m$) :: \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle \rightarrow$ }\\
\text{$\langle$[\ACCOUNTS, \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle$}}} 
\end{equation}
~\\
~\\
Rule 5 [rejected of public key]:

\begin{equation}{}
\frac{\text{$\neg$ checkPub(\MANAGERS, $pkh'$)}}{\parbox{4.2in}{\text{$\langle$[\ACCOUNTS, (transfer $n$ from $pkh$ to $pkh'$ fee $m$) :: \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle \rightarrow$ }\\
\text{$\langle$[\ACCOUNTS, \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle$}}} 
\end{equation}
~\\
~\\
Rule 6 [included]:
\begin{equation}{}
\frac{}{\parbox{4.2in}{\text{[$<$ transfer $n$ from $puk$ to  $puk'$ fee $m$, oph, \TIME $>$ :: \PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME' ] $\rightarrow$ } \\
 \text{[\PENDING, $<$ transfer $n$ from  $puk$ to $puk'$ fee $m$, oph, \TIME' $>$ :: \ACCEPTED, updateSucc(\MANAGERS, } \\
\text{$puk, puk', n, m$), \CONTRACTORS, \TIME' + 1]}}} 
\end{equation}
~\\
Rule 7 [timeout]:
\begin{equation}{}
\frac{\text{\TIME' - \TIME $\ge$ 60}}{\parbox{4.2in}{\text{[$<$ transfer $n$ from $puk$ to  $puk'$ fee $m$, oph, \TIME $>$ :: \PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME' ] $\rightarrow$} \\
 \hspace*{0cm} \text{[\PENDING, \ACCEPTED, updateCou(\MANAGERS, $puk$, False), \CONTRACTORS, \TIME']}}} 
\end{equation}

@@

\begin{equation}{}
\frac{\text{checkAcc($pkh$, \ACCOUNTS) $\wedge$ checkId($id$, \CONTRACTS)}}{\parbox{4.2in}{\text{$\langle$[\ACCOUNTS, \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle \rightarrow \langle$[\ACCOUNTS, (originate contract ${id}$ transferring} \\
  \text{${n}$ from ${pkh}$} \text{running ${code}$ init ${s}$) :: \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle$}}} 
\end{equation}
~\\
~\\
Rule 2 [injected]:

\begin{equation}{}
\frac{\text{checkBan(\MANAGERS, $pkh, n, m$) $\wedge$ checkCou(\MANAGERS, $pkh$) $\wedge$ \text{checkPrg($code, s$)}}}{\parbox{4.2in}{\text{$\langle$[\ACCOUNTS, (originate contract ${id}$ transferring  ${n}$ from ${pkh}$ running ${code}$ init ${s}$)} \text{ :: \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME] $\rangle \rightarrow \langle$ [\ACCOUNTS, \OPERATIONS, \CONTRACTS],} \text{[(originate contract ${id}$ transferring ${n}$ from ${pkh}$ running ${code}$ init ${s}$)} \text{:: \PENDING, \ACCEPTED, updateCou(\MANAGERS, $pkh$, True), \CONTRACTORS, \TIME] $\rangle$}}} 
\end{equation}
~\\
~\\
Rule 3 [rejected of code]:

\begin{equation}{}
\frac{\text{$\neg$ checkPrg($code, s$)}}{\parbox{4.2in}{\text{$\langle$[\ACCOUNTS, (originate contract ${id}$ transferring  ${n}$ from ${pkh}$ running ${code}$ init ${s}$)} \text{:: \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle \rightarrow \langle$[\ACCOUNTS, \OPERATIONS, \CONTRACTS],} \text{[\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle$}}} 
\end{equation}
~\\
~\\
Rule 4 [rejected of counter]:

\begin{equation}{}
\frac{\text{$\neg$ checkCou(\MANAGERS, $pkh$)}}{\parbox{4.2in}{\text{$\langle$[\ACCOUNTS, (originate contract ${id}$ transferring  ${n}$ from ${pkh}$ running ${code}$ init ${s}$))} \text{:: \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle \rightarrow \langle$ [\ACCOUNTS, \OPERATIONS, \CONTRACTS],} \text{[\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle$}}} 
\end{equation}
~\\
~\\
Rule 5 [rejected of balance]:

\begin{equation}{}
\frac{\text{$\neg$ checkBan(\MANAGERS, $pkh, n, m$)}}{\parbox{4.2in}{\text{$\langle$[\ACCOUNTS, (originate contract ${id}$ transferring  ${n}$ from ${pkh}$ running ${code}$ init ${s}$)} \text{:: \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle \rightarrow \langle$[\ACCOUNTS, \OPERATIONS, \CONTRACTS],} \text{[\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle$}}} 
\end{equation}
~\\
~\\
Rule 6 [included]:
\begin{equation}{}
\frac{}{\parbox{4.2in}{\text{$\langle$[\ACCOUNTS, \OPERATIONS, \CONTRACTS], [$<$ (originate contract ${id}$ transferring  ${n}$ from ${pkh}$ running } \\
\text{${code}$ init ${s}$), \TIME $>$ :: \PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME' ]$\rangle \rightarrow \langle$[\ACCOUNTS, \OPERATIONS,($< id$, } \\
\text{generateHash($id, code, s$, \TIME'), $code >$ :: \CONTRACTS)], [\PENDING, $<$ (originate contract ${id}$ } \\
\text{transferring  ${n}$ from ${pkh}$ running ${code}$ init ${s}$), \TIME' $>$ :: \ACCEPTED, updateSucc(\MANAGERS, } \\
\text{$puk, n, m$), ($<$ generateHash($id, code, s$, \TIME'), $n, code$, } \\
 \text{getStorage($code, s$) $>$) :: \CONTRACTORS), \TIME' + 1]$\rangle$}}} 
\end{equation}
~\\
Rule 7 [timeout]:
\begin{equation}{}
\frac{\text{\TIME' - \TIME $\ge$ 60}}{\parbox{4.2in}{\text{[$<$ (originate contract ${id}$ transferring  ${n}$ from ${pkh}$ running ${code}$ init ${s}$) $>$ } \\
\text{:: \PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME' ] $\rightarrow$[\PENDING, \ACCEPTED, updateCou(\MANAGERS, $puk$, False), \CONTRACTORS, \TIME']}}} 
\end{equation}
~\\
~\\
B. \textbf{Transfer}
\\
~\\
Rule 1 [proposal]:

\begin{equation}{}
\frac{\text{checkAcc($pkh$, \ACCOUNTS)  }}{\parbox{4.2in}{\text{$\langle$[\ACCOUNTS, \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle \rightarrow \langle$[\ACCOUNTS, (transfer ${n}$ from ${pkh}$ to  ${puh}$ arg ${s}$ }  \\
\text{fee ${m}$) :: \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle$}}} 
\end{equation}
~\\
~\\
Rule 2 [injected]:

\begin{equation}{}
\frac{\text{checkBan(\MANAGERS, $pkh, n, m$) $\wedge$ checkCou(\MANAGERS, $pkh$) $\wedge$ checkPuh(\CONTRACTORS, $puh$)}
\\
\text{ $\wedge$ checkArg(\CONTRACTORS, $puh, s$)}}{\parbox{4.2in}{\text{$\langle$[\ACCOUNTS, (transfer ${n}$ from ${pkh}$ to  ${puh}$ arg ${s}$ fee ${m}$) :: \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle$}\\
\text{$\rightarrow$  $\langle$[\ACCOUNTS, \OPERATIONS, \CONTRACTS], [($<$ (transfer ${n}$ from ${pkh}$ to  ${puh}$ arg ${s}$ fee ${m}$), }\\
 \text{generateOph($pkh, puh, s, n, m$, \TIME), \TIME $>$) :: \PENDING, \ACCEPTED, updateCou(\MANAGERS, $pkh$, True), }\\
\text{\CONTRACTORS, \TIME] $\rangle$}}} 
\end{equation}
~\\
~\\
Rule 3 [rejected of counter]:

\begin{equation}{}
\frac{\text{$\neg$ checkCou(\MANAGERS, $pkh$)}}{\parbox{4.2in}{\text{$\langle$[\ACCOUNTS, (transfer ${n}$ from ${pkh}$ to  ${puh}$ arg ${s}$ fee ${m}$) :: \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle$  }\\
\text{$\rightarrow \langle$[\ACCOUNTS, \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle$}}} 
\end{equation}
~\\
~\\
Rule 4 [rejected of balance]:

\begin{equation}{}
\frac{\text{$\neg$ checkBan(\MANAGERS, $pkh, n, m$)}}{\parbox{4.2in}{\text{$\langle$[\ACCOUNTS, (transfer ${n}$ from ${pkh}$ to  ${puh}$ arg ${s}$ fee ${m}$) :: \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle$ }\\
\text{$\rightarrow \langle$[\ACCOUNTS, \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle$}}} 
\end{equation}
~\\
~\\
Rule 5 [rejected of public hash]:

\begin{equation}{}
\frac{\text{$\neg$ checkPuh(\CONTRACTORS, $puh$)}}{\parbox{4.2in}{\text{$\langle$[\ACCOUNTS, (transfer ${n}$ from ${pkh}$ to  ${puh}$ arg ${s}$ fee ${m}$) :: \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle$ }\\
\text{$\rightarrow \langle$[\ACCOUNTS, \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle$}}} 
\end{equation}
~\\
~\\
Rule 6 [rejected of argument]:
